Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
oops

\documentclass[11pt,twocolumn]{article} 
\usepackage{simpleConference}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{url,hyperref}
\usepackage{tikz,pgfplots}

@@

\author{Calvin Huang (calvinh@mit.edu)\\
    Brian Shimanuki (bshimanuki@mit.edu)\\
    Charlotte Chen (czchen@mit.edu)
\\
}

@@

We found that adding the additional Turkish candidates and features regarding translation
did not help accuracy of training very much; this is likely due to the incompleteness of the translation
dictionary only being able to provide potential translations for very few words, and due to the ambiguity
of translation, it's very hard to tell whether or not something would make a good parent of a word after
translating the word into Turkish, taking the parent in Turkish, and translating it back.
\bibliography{paper}
\bibliographystyle{plainnat}

>>>>

\documentclass[11pt,twocolumn]{article} 
\usepackage[utf8]{inputenc}
\usepackage{simpleConference}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{url,hyperref}
\usepackage{tikz,pgfplots}

@@

\author{Calvin Huang (calvinh@mit.edu), 6.867\\
    Brian Shimanuki (bshimanuki@mit.edu), 6.867\\
    Charlotte Chen (czchen@mit.edu), 6.806\\
}

@@

It should be noted that as $\alpha$ increases, the likelihood of the labeled training data matters more and more,
and the score is positively influenced up to a point---as $\alpha$ increases further, the labeled data
dominates the loss function, and the information from the unstructured model ceases to be used,
causing a slow decline in the score.

We found that adding the additional Turkish candidates and features regarding translation
did not help accuracy of training very much; this is likely due to the incompleteness of the translation
dictionary only being able to provide potential translations for very few words. Furthermore, due to the ambiguity
of translation, it's very hard to tell whether or not something would make a good parent of a word after
translating the word into Turkish, taking the parent in Turkish, and translating it back. The additional candidates,
for the most part, reduced accuracy by increasing the number of incorrect parent choices,
as opposed to their intended result of providing parents that our candidate generation algorithms missed.
\bibliography{paper}
\bibliographystyle{plainnat}
